Inference failure: Confound and control in BBS experiments

### 2016-05-09 simulation/statfail.Rmd
bug fix in aggregation/graphics

      ## the acceptances based on the pretest
      not_rejected <- (input$n.sims - rejections) / input$n.sims
      feature_relevant_in_multiple <- sum(with(subset(cmp,!pretest), feature.multiple)) / input$n.sims
      manipulation_only_in_simple <-  sum(with(subset(cmp,!pretest), manipulation.simple & !manipulation.multiple)) / input$n.sims

>>>>

      ## the acceptances based on the pretest
      not_rejected <-  sum(!cmp$pretest) / input$n.sims
      feature_relevant_in_multiple <- sum(with(subset(cmp,!pretest), feature.multiple)) / input$n.sims
      manipulation_only_in_simple <-  sum(with(subset(cmp,!pretest), manipulation.simple & !manipulation.multiple)) / input$n.sims
